The K2 Bright Star Survey I: Methodology and Data Release

### 2019-07-12 paper/ms.tex
hogg edits

% describe halo algorithm
The `TV-min' halo method was first described by \citet{White2017} and applied to the Pleiades' Seven Sisters. It was also applied to Aldebaran with further developments by \citet{Farr2018}. We follow the Optimized-Weight Linear (OWL) photometry concept described by Hogg \&  Foreman-Mackey (2014, unpublished: preprint  \href{https://github.com/davidwhogg/OWL/}{\nolinkurl{github.com/davidwhogg/OWL/}}) in our assumptions. We assume that a star has a wide PSF sampled by many pixels with different sensitivities, which moves around on the detector within a small region and which may vary to a small extent in time. We assume that our time series consists of many epochs sampled with a nearly even cadence. We do not have metadata describing the spacecraft motion, pixel gains, PSF variations or other noise processes. Because photometry is a linear operation, any estimator of the flux is necessarily a weighted sum of pixel values, which we choose to be time-invariant but note that this strong constraint is not necessary in general.

The additional constraint beyond the OWL axioms is that some pixels are saturated, so that SAP is not possible. Instead the measurements are made using the unsaturated pixels $p_j$ at the wings of the broad and structured PSF. We construct a light curve as a linear combination of these time series with weights $w_j$, so that flux at epoch $i$ is

@@

\begin{equation}
    Q_{k,l} \equiv {\sum_i{|f_i - f_{i-\delta}|^k}},
\end{equation}

\noindent subject to the constraints

@@

This is a classic convex optimization program with constraints, which we solve with the \texttt{scipy} \citep{scipy} L-BFGS-B nonlinear optimization code \citep{lbfgsb}. $Q_{k,l}$ has analytic derivatives with respect to $w_j$ \citep[calculated with \texttt{autograd};][]{autograd}, and it is therefore extremely fast to optimize and converges well on a global solution. In practice, for computational reasons we optimize over parameters $\tilde{w}_j$ such that $w_j = \text{softmax}(\tilde{w}_j)$, as this satisfies the constraint that $\forall_j w_j > 0$, and while this also constrains their sum to be unity, we renormalize $f$ to satisfy its normalization constraint before calculating the objective function and this additional constraint is removed again.

The objective function $Q_{k,l}$ is the $L_k$ norm on a `lagged' finite difference with a lag parameter $\delta$. For $k = 1$ and $\delta = 1$, $Q_{1,1}$ is the standard Total Variation objective (TV) used in previous halo papers \citep[e.g.][]{White2017,Farr2018}, and can be seen as the L1 norm on the derivative of $f$ or as a discrete approximation to its arc length. The L2 Variation (L2V) with $k=2$ is sometimes referred to in image processing literature as the `smoothness' regularizer, as it seeks to penalize large gradients without necessarily making them sparse. The lag parameter $\delta$ allows for flexibility in modelling systematics occurring at different timescales from epoch-to-epoch, and we investigate its effects below. The order parameter $k$ allows for flexibility in how sensitive we are to normally-distributed versus long-tailed noise. For convenience in the rest of this paper, we will refer to the $k=1$ case as TV, the $k=2$ case as L2V, and the $k=3$ case as L3V.

>>>>

% describe halo algorithm
The `TV-min' halo method was first described by \citet{White2017} and applied to the Pleiades' Seven Sisters. It was also applied to Aldebaran with further developments by \citet{Farr2018}. We follow the Optimized-Weight Linear (OWL) photometry concept described by Hogg \&  Foreman-Mackey (2014, unpublished: preprint  \href{https://github.com/davidwhogg/OWL/}{\nolinkurl{github.com/davidwhogg/OWL/}}) in our assumptions. We assume that a star has a wide PSF sampled by many pixels with different sensitivities. This PSF varies at most to a small extent in time. The star moves around on the detector within a small region. We assume that our time series consists of many epochs sampled with a nearly even cadence. We do not have metadata describing the spacecraft motion, pixel gains, PSF variations or other noise processes. Because photometry is a linear operation, any estimator of the flux is necessarily a weighted sum of pixel values, which we choose to be time-invariant but note that this strong constraint is not necessary in general. In OWL and here, we search for a linear combination of pixels that is invariant with respect to the the noise processes but accurately preserved astrophysical signals.

The additional constraint beyond the OWL axioms is that some pixels are saturated, so that Simple Aperture Photometry (SAP) is inadvisable. Instead the measurements are made using the unsaturated pixels $p_j$ at the wings of the broad and structured PSF. We construct a light curve as a linear combination of these time series with weights $w_j$, so that flux $f_i$ at epoch $i$ is

@@

\begin{equation}
    Q_{k,\delta} \equiv {\sum_i{|f_i - f_{i-\delta}|^k}},
\end{equation}

\noindent with an integer lag parameter $\delta$ and an integer $L_k$ norm, subject to the constraints

@@

This is a classic convex optimization program with constraints, which we solve with the \texttt{scipy} \citep{scipy} L-BFGS-B nonlinear optimization code \citep{lbfgsb}. $Q_{k,\delta}$ has analytic derivatives with respect to $w_j$ \citep[calculated with \texttt{autograd};][]{autograd}, and it is therefore extremely fast to optimize and converges well on a global solution. In practice, for computational reasons we optimize over parameters $\tilde{w}_j$ such that $w_j = \text{softmax}(\tilde{w}_j)$, as this satisfies the constraint that $\forall_j w_j > 0$, and while this also constrains their sum to be unity, we renormalize $f$ to satisfy its normalization constraint before calculating the objective function and this additional constraint is removed again.

The objective function $Q_{k,\delta}$ is the $L_k$ norm on a `lagged' finite difference with a lag parameter $\delta$. For $k = 1$ and $\delta = 1$, $Q_{1,1}$ is the standard Total Variation objective (TV) used in previous halo papers \citep[e.g.][]{White2017,Farr2018}, and can be seen as the L1 norm on the derivative of $f$ or as a discrete approximation to its arc length. The L2 Variation (L2V) with $k=2$ is sometimes referred to in image processing literature as the `smoothness' regularizer, as it seeks to penalize large gradients without necessarily making them sparse. The lag parameter $\delta$ allows for flexibility in modelling systematics occurring at different timescales from epoch-to-epoch, and we investigate its effects below. The order parameter $k$ allows for flexibility in how sensitive we are to normally-distributed versus long-tailed noise. For convenience in the rest of this paper, we will refer to the $k=1$ case as TV, the $k=2$ case as L2V, and the $k=3$ case as L3V.
